R Notebook

### 2018-10-08 analysis/talk-figures.Rmd
update model results and analyses

```{r fighabfreq_predictive_vs_past, cache = F}
fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary %>%
                                            ungroup() %>%
                                            mutate(condition = factor(condition,
                                                                      levels = c("preventative", "baseline", "enabling"))) %>%
                                            mutate(src = 'Manipulation check'),
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), size = 4,
              color = 'white')+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'white')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  facet_wrap(~src)+
  guides(fill=guide_legend(reverse = T), shape=guide_legend(reverse = T))+
  scale_fill_brewer(type = "seq", palette = 2)+
  xlab("Past frequency")+
  ylab("Predicted frequency")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.x = element_text(vjust = 1),
        axis.title.y = element_text(vjust = 1))

@@

ggsave(fig.hab.freq.predictive.vs.past, 
       file = paste(fig.path, "habituals_predictives_manipCheck.pdf", sep =""),
       width = 6, height = 4)
```

@@

```{r habituals-predictive-endorsement-scatters, cache = F}
habituals.endorsement.pred.scatters <- m.hab.predictive.endorse.allModels %>%
  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
         src =factor(src , levels = c("human data", "regression_pastfreq",
                                     "past_model", "regression_futurefreq",
                                      "predictive_model"),
                     labels= c("Human data","regression_pastfreq", 
                                "Uncertain semantics (Past)", "Linear model (Predictive frequency)","Uncertain semantics (Predictive)"))) %>%
  filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
ggplot(., 
       aes (x = MAP, xmin = cred_lower, xmax = cred_upper, 
            y = MAP_h, ymin= low, ymax = high, fill = condition,
            shape = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3, color = 'white')+
  #geom_linerange(alpha = 0.15)+
  #geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
  geom_linerange(alpha = 0.5, size = 1, color = 'white')+
  geom_errorbarh(color = 'white', alpha = 0.5)+
  geom_point(size = 3, color ='white')+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_shape_manual(values=c(21,22,23))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_brewer(type = "seq", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Model prediction")+
  facet_grid(.~src)+
  theme(legend.position = "right")

ggsave(habituals.endorsement.pred.scatters, 
       file = paste(fig.path, "habituals_predictive_modelScatters.pdf", sep =""),
       width = 10, height = 5)
```

@@

>>>>

```{r fighabfreq_predictive_vs_past, cache = F}
fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary %>%
                                            ungroup() %>%
                                            mutate(condition = factor(condition,
                                                                      levels = c("preventative", "baseline", "enabling"))) %>%
                                            mutate(src = 'Manipulation check'),
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), size = 4,
              color = 'white')+
  scale_shape_manual(values=c(21,21,21))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'white')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  facet_wrap(~src)+
  guides(fill=guide_legend(reverse = T), shape=guide_legend(reverse = T))+
  scale_fill_brewer(type = "qual", palette = 2)+
  xlab("Past frequency")+
  ylab("Predicted frequency")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title.x = element_text(vjust = 1),
        axis.title.y = element_text(vjust = 1))

@@

ggsave(fig.hab.freq.predictive.vs.past,
       file = paste(fig.path, "habituals_predictives_manipCheck.pdf", sep =""),
       width = 6, height = 4)
```
```{r}
d.hab.predictive.endorsment.condition.summary
```

```{r}
d.hab.predictive.endorsment.condition.summary %>%
    mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling"))) %>%
    ggplot(., aes(x=condition, y=MAP_h, 
                 fill=condition, shape=condition,
                 ymin=low, ymax = high))+
  geom_col(position = position_dodge(0.5), color = 'white', width = 0.5)+
  geom_errorbar(alpha = 1, size = 0.5, position = position_dodge(0.3),
                width = 0.2,
                 color = 'white')+
  #geom_point(shape = 21, size = 3)+
  #scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_viridis(discrete = T)+
  scale_fill_brewer(type = "qual", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  #coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("")+
  theme(strip.text.y = element_text(hjust = 0, angle = 0),#, vjust = 1),
        axis.text.x = element_text(vjust = 1, hjust = 1, angle = 45,
                                   lineheight = 0.7),
        legend.position = "none")
ggsave(file = paste(fig.path, "habituals_predictives_conditionEndorse.pdf", sep =""),
       width = 3.5, height = 3)
```

@@

```{r habituals-predictive-endorsement-scatters, cache = F}
habituals.endorsement.pred.scatters <- m.hab.predictive.endorse.allModels %>%
  mutate(condition = factor(condition, levels = c("preventative", "baseline", "enabling")),
         src =factor(src , levels = c("human data", "regression_pastfreq",
                                     "past_model", "regression_futurefreq",
                                      "predictive_model"),
                     labels= c("Human data","regression_pastfreq", 
                              "Generics Model\n Past Frequency", 
                              "Frequency alone\n Predictive Frequency",
                              "Generics Mçodel\n Predictive Frequency"))) %>%
  filter(!(src %in% c("Human data", "regression_pastfreq"))) %>%
ggplot(., 
       aes (x = MAP, xmin = cred_lower, xmax = cred_upper, 
            y = MAP_h, ymin= low, ymax = high, fill = condition,
            shape = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3, color = 'white')+
  #geom_linerange(alpha = 0.15)+
  #geom_col(position = position_dodge(0.7), color = 'black', width = 0.7)+
  geom_linerange(alpha = 0.5, size = 1, color = 'white')+
  geom_errorbarh(color = 'white', alpha = 0.5)+
  geom_point(size = 3, color ='white')+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_shape_manual(values=c(21,21,21))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  scale_fill_brewer(type = "qual", palette = 2)+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  ylab("Habitual endorsement")+
  xlab("Model prediction")+
  facet_wrap(~src, nrow = 1)+
  theme(legend.position = "right")

habituals.endorsement.pred.scatters

ggsave(habituals.endorsement.pred.scatters, 
       file = paste(fig.path, "habituals_predictive_modelScatters.pdf", sep =""),
       width = 8, height = 5)
```

@@

```{r figure-causals-priors, fig.caption = "Four background distributions participants were exposed to in Expt. 3 (stimuli) and priors reconstructed from participants' responses (model). ", fig.width = 8, fig.height = 3, eval = F}
sample.dists <- bind_rows(
  data.frame(
    dist = "rare weak",
    x = c(rbeta(n = 3000, shape1 = 20, shape2 = 100),
          rbeta(n = 7000, shape1 = 1, shape2 = 100)
          )
  ),
  data.frame(
    dist = "common weak",
    x = rbeta(n = 10000, shape1 = 20, shape2 = 100)
  ),
  data.frame(
    dist = "rare deterministic",
    x = c(rbeta(n = 3000, shape1 = 100, shape2 = 2),
          rbeta(n = 7000, shape1 = 1, shape2 = 100)
          )
  ),
  data.frame(
    dist = "common deterministic",
    x = rbeta(n = 10000, shape1 = 100, shape2 = 2)
  )
) %>%
    mutate(Distribution = 
        factor(dist, levels = c(  "rare weak", "common weak","rare deterministic","common deterministic"),
         labels = c("Rare Weak", "Common Weak", "Rare Strong", "Common Strong")))

figure.causals.priors <- sample.dists %>%
  ggplot(., aes(x = x*100, fill = Distribution, color = Distribution))+ 
  geom_density( adjust = 1.3, 
               size = 1.2,
               aes( y = ..scaled..), color = 'white')+ #
  scale_x_continuous(limits = c(0, 100), breaks = c(0, 50, 100))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  #scale_fill_manual(values = c("#636363", "#d7191c"))+#, "#2b83ba"))+
  scale_fill_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
  #scale_color_manual(values = c("#636363", "#d7191c"))+
  #scale_alpha_manual(values = c(0.1, 0.4))+
  #scale_linetype_manual(values = c(2, 1))+
  ylab("Scaled Prior Probability")+
  xlab("Prevalence")+
  facet_wrap(~Distribution, scales = 'free', nrow = 2)+
  guides(fill = F, color = F)+
  theme(legend.position = 'bottom', legend.direction = 'horizontal')

ggsave(figure.causals.priors,
         file = paste(fig.path, "causals-priors_stimuli.pdf", sep = ""), 
       width =6, height = 4)
```
